Astr 513: Final Project

### 2016-05-05 Final_Project/ms.tex
Wrote the likelihood section.

\section{Distance Modulus Model}
\label{sec:model}
The main objective of \citet{betoule2014} and \citet{rest2014} is 
to place constraints on cosmological parameters $\Omega_M$, $\Omega_\Lambda$, 
$\Omega_k$, and $w$. In order to so, we must examine the relationship between distance 
modulus and cosmology. The distance modulus $\mu$ is determined from 
the luminosity distance $d_L$ by 
\begin{equation}
\label{eq:mu_dL}
\mu=5 \log\left(\frac{d_L}{1 \mathrm{Mpc}}\right)+25. 
\end{equation}
The luminosity distance depends on the cosmology by 
\begin{equation}
\label{eq:luminosityDistance}
d_L(z; w, \Omega_M, \Omega_\Lambda, H_0)= (1+z)|\Omega_k|^{-1/2}\mathcal{S}_{k}\displaystyle\left[c|\Omega_k|^{1/2}\int_{0}^{z}\frac{dz'}{H(z')}\right],
\end{equation}
where $\Omega_k \equiv 1-\Omega_M-\Omega_{\Lambda}$. The function 
$\mathcal{S}_{k}$ depends on the curvature density $\Omega_k$ in that 
\[
    \mathcal{S}_{k}= 
\begin{cases}
    \text{sin}(x),&  \Omega_k < 0\\
    x,& \Omega_k = 0\\
    \text{sinh}(x),& \Omega_k > 0
\end{cases}.
\]
The function $H(z)$ is expressed as 
\begin{equation}
\label{eq:hubbleFunction}
H(z)= H_0\displaystyle\left[\Omega_M(1+z)^3+\Omega_{\Lambda}(1+z)^{3(1+w)}+\Omega_k(1+z)^2\right]^{1/2},
\end{equation} where the Hubble constant $H_0$ can be written in terms of a dimensionless Hubble parameter $h$ by $H_0=100h \mathrm{kms^{-1}Mpc^{-1}}$.

@@

\subsection{Likelihood}
\label{sec:likelihood}
\TM{This has our likelihood.}

\subsection{Planck Priors}
\label{sec:planck_priors}

>>>>

\section{Distance Modulus Model}
\label{sec:model}
The main objective of \citet{betoule2014} and \citet{rest2014} is 
to place constraints on cosmological parameters $\Omega_M$, $\Omega_\Lambda$, 
$\Omega_k$, and $w$. In order to so, we must examine the relationship between distance 
modulus and cosmology. The distance modulus $\mu$ is determined from 
the luminosity distance $d_L$ by 
\begin{equation}
\label{eq:mu_dL}
\mu=5 \log\left(\frac{d_L}{1 \mathrm{Mpc}}\right)+25. 
\end{equation}
The luminosity distance depends on the cosmology by 
\begin{equation}
\label{eq:luminosityDistance}
d_L(z; w, \Omega_M, \Omega_\Lambda, H_0)= (1+z)|\Omega_k|^{-1/2}\mathcal{S}_{k}\displaystyle\left[c|\Omega_k|^{1/2}\int_{0}^{z}\frac{dz'}{H(z')}\right],
\end{equation}
where $\Omega_k \equiv 1-\Omega_M-\Omega_{\Lambda}$. The function 
$\mathcal{S}_{k}$ depends on the curvature density $\Omega_k$ in that 
\[
    \mathcal{S}_{k}= 
\begin{cases}
    \text{sin}(x),&  \Omega_k < 0\\
    x,& \Omega_k = 0\\
    \text{sinh}(x),& \Omega_k > 0
\end{cases}.
\]
The function $H(z)$ is expressed as 
\begin{equation}
\label{eq:hubbleFunction}
H(z)= H_0\displaystyle\left[\Omega_M(1+z)^3+\Omega_{\Lambda}(1+z)^{3(1+w)}+\Omega_k(1+z)^2\right]^{1/2},
\end{equation} where the Hubble constant $H_0$ can be written in terms of a 
dimensionless Hubble parameter $h$ by $H_0=100h \mathrm{km\ s^{-1}Mpc^{-1}}$.

@@

\subsection{Likelihood}
\label{sec:likelihood}
Using the above model for the distance modulus allows us to write a
probability that a model can generate our data:
%
\begin{equation}
  \label{eq:likelihood}
  P(\mu(z)|\mathrm{cos}) = \frac{1}{\sqrt{2\pi|\mathbf{C}|}}\exp
  \left[-\frac{1}{2}\sum_{i,j=0}^{N_{samples}}\left(\mu(z) - \mu_{\mathrm{model}}(z)\right)_i\mathbf{C}^{-1}_{i,j}\left(\mu(z) - \mu_{\mathrm{model}}(z)\right)_j\right]
\end{equation}
%
where $\mathbf{C}$ is the full covariance matrix between all of the $N_{samples}$ 
in the data, and $\mathrm{cos}$ represents the cosmology that we are investigating
(e.g. flat $\Lambda$CDM, $wCDM$, etc.). 
This is not the full picture though, since we must employ
Bayes' Theorum in order to include any priors on our choice of 
parameters and recover the posterior distribution function of our
parameters given our data
%
\begin{equation}
  \label{eq:posterior}
  P(\mathrm{cos}|\mu(z)) = P_{prior}(\mathrm{cos}) P(\mu(z)|\mathrm{cos}).
\end{equation}
%
For this work we investigate a combination of priors. \Cosmosis is implemented
in a way that requires the user to provide bounds on the parameter space, which we
detail for each parameter in Table~XXX
\TM{Make this table. Just look at the cosmology.ini files.}
Within those bounds, we investigated using a flat prior $P_{prior}=1$ and
\Planck priors.

\subsection{Planck Priors}
\label{sec:planck_priors}
\TM{The only thing we really require is a corner plot of {\it just} the priors.}
